Opportunities for improvement in the care of adult trauma patients arriving in shock

### 2024-11-08 thesis.Rmd
la till alla tabeller o dånt

@@

>>>>

```{r sample-characteristics, echo=FALSE}
sample.characteristics.table
sample.characteristics.tableBE
sample.characteristics.tableSBP
```

@@

```{r BE-subofi, echo=FALSE}
print(p)
```

Table 5

```{r SBP-subofi, echo=FALSE}
print(pSBP)
```

Table 6 - Subofi detailed

```{r SBP-subofi-detailed, echo=FALSE}
print(pd)
```

```{r BE-subofi-detailed, echo=FALSE}
print(pSBPd)
```

Table adjusted log
```{r Adjusted_log, echo=FALSE}
log_regBE_sample.characteristics.table
log_regSBP_sample.characteristics.table
```

Table unadjusted log
```{r Unadjusted_log, echo=FALSE}
log_regBE_sample.characteristics.table_unadjusted
log_regSBP_sample.characteristics.table_unadjusted
```
